Eliminating object prior-bias from sparse-projection tomographic reconstructions

### 2022-02-07 paper/post_tci.tex
updated the results sections based on our discussion.

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  Tomographic reconstruction from undersampled measurements is a
  necessity when the measurement process is potentially harmful, needs
  to be rapid, or is resource-expensive. In such cases, information
  from previously existing longitudinal scans of the same object
  (`object-prior') helps in the reconstruction of the current object
  (`test') from its significantly fewer measurements. A common problem
  with these techniques is the strong influence of object-priors in
  the reconstruction of new changes in the test.  In this work, we
  mitigate this problem by first estimating the location of changes (`new
  regions') and then imposing object-prior in \textit{only} those regions
  which are similar to the prior (`old regions').

@@

In this section, we first illustrate the advantage of using multiple
types of eigenspaces for the computation of weights map, and then
present reconstruction results on all datasets. We show both
qualitative and quantitative results. For the latter,
we use two metrics: the Root Mean Squared Error (RMSE) and the
Structural Similarity Index Metric (SSIM)~\cite{ssim}. 
% If
% $\boldsymbol{x}$ is the groundtruth data with $N$ voxels and
% $\hat{\boldsymbol{x}}$ is the reconstructed data, then RMSE is
% computed as follows

% \begin{equation}
%   \textrm{RMSE} =\sqrt{\frac{1}{N}\sum_{i=1}^N(\boldsymbol{x}(i) -
%     \hat{\boldsymbol{x}}(i))^2}.
%  \end{equation}
RMSE corresponds to error in intensity values and is a measure of
absolute error. For purposes of normalization, while reporting numbers
we rescale intensity values of both the ground truth and the
reconstructed results to lie between 0 to 1, so that the best possible
RMSE is 0, and the worst value is 1.  On the other hand, SSIM seeks to
consider perceptual changes, as well as correlation between adjacent
pixels. This can be useful in a clinical context. The SSIM~\cite{multiscale_ssim} also provides a flexibility to set coefficients for the following three factors: Structure, Contrast and Intensity. In all our results, we report SSIM with both the standard setting, i.e., with coefficients $1.0,1.0,1.0$ and a structure-focussed setting, wherein we assign a higher weightage to structure preservation. In the latter case, we assign the following coefficients to the factors Structure, Contrast, and Intensity respectively: $0.7,0.2,0.1$. Our results are optimized for structure-focussed SSIM, but
it can be verified that in all cases for the various datasets
considered, our results are favourable with either metric.

Here below, we first discuss tuning of parameters followed by the
rationale for using multiple eigenspaces to compute weightsmap. We
then present reconstruction results for each of the datasets.
%The reason for emphasizing the structure with an
%exponent of 0.7 stems from the optimization process since the
%intensity span (and, in general, the histogram) of reconstructed volumes
%differ across various methods and solvers.

\subsection{Tuning of parameters}
\label{sec:tuning_parameters}
The aim of our experiments is to demonstrate the benefit of using weighted prior reconstruction when optimal hyperparameter values for $\lambda_1$, $\lambda_2$ and $k$ are chosen.  In this regard, we assume the ground-truth to be known. Specifically, $\lambda_1$ was tuned to maximize the
SSIM of the complete reconstructed test volume using the TV-only
regularizer.  In particular, regions of interest (RoI) are 
not known in advance, and thus not considered for the purpose of this
tuning. This optimal $\lambda_1$ was retained for spatially-varying prior-based reconstruction. With the already chosen optimal $\lambda_1$, we apply our method for a range of $\lambda_2$ values and select the one that gives the best SSIM with reference to the ground truth. %The value of $\lambda_2$ influences the amount of artefacts that can be removed by the use of object-prior at the expense of its dominance in new regions. %This value was found to lie between $(0,3)$ for our datasets.
%In principle, one could have jointly optimized both $\lambda_1$ and $\lambda_2$ to get even better results compared to the one we have in Sections~\ref{sec:results_with_imaging_model}, and~\ref{sec:results_without_imaging_model}. 
In practice however, since ground-truth will never be available, these parameters must be tuned using only the set of templates available.  One of the templates can be assumed to be a pseudo-test, and a grid search can be performed to get the best possible hyperparameter values. These values can then be used for reconstructing the `real' test volume.

%in the nvone may select $\lambda_2$ omnisciently only while imaging a particular class of object (say `sprouts') for the first time, and thereafter retain the same $\lambda_2$ while imaging other objects of the same class in future.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  Tomographic reconstruction from undersampled measurements is a
  necessity when the measurement process is potentially harmful, needs
  to be rapid, or is resource-expensive. In such cases, information
  from previously existing longitudinal scans of the same object
  (`object-prior') helps in the reconstruction of the current object
  (`test') from its significantly fewer measurements. A common problem
  with these techniques is the %strong 
  influence of object-priors in
  the reconstruction of new changes in the test.  In this work, we
  mitigate this problem by first estimating the location of changes (`new
  regions') and then imposing object-prior in \textit{only} those regions
  which are similar to the prior (`old regions').

@@

In this section, we first illustrate the advantage of using multiple
types of eigenspaces for the computation of weights map, and then
present reconstruction results on all datasets.  We show both
qualitative and quantitative results.  Before we do this, it is import
to first consider our method of reporting our results.

\subsection{Metrics}
In order to show the efficacy, we will clearly need to have either a
gold-standard method, or a ground truth reference reconstruction such
as those described in Sec~\ref{sec:datasets} (see, for example, the
top left figure in Fig.~\ref{fig:story}).  For quantitative results,
we use two metrics: the Root Mean Squared Error (RMSE) and the
Structural Similarity Index Metric (SSIM)~\cite{ssim}.
% If
% $\boldsymbol{x}$ is the groundtruth data with $N$ voxels and
% $\hat{\boldsymbol{x}}$ is the reconstructed data, then RMSE is
% computed as follows

% \begin{equation}
%   \textrm{RMSE} =\sqrt{\frac{1}{N}\sum_{i=1}^N(\boldsymbol{x}(i) -
%     \hat{\boldsymbol{x}}(i))^2}.
%  \end{equation}
RMSE corresponds to error in intensity values and is a measure of
absolute error. Our results depend on the optimization library (as
mentioned earlier) \cite{TVReg-lib}; however, the range of values
returned by other libraries (such as the Matlab implementation of FDK
used in our ground truth reconstructions) are not compatible with
these.  This is not an issue for qualtitative results since the
display program compensates for range differences. For RMSE, and
for purposes of normalization and a fair comparison, while reporting
numbers, we therefore rescale intensity values of both the ground
truth and the reconstructed results to lie between 0 to 1, so that the
best possible RMSE is 0, and the worst value is 1.

On the other hand, SSIM seeks to consider perceptual changes, as well
as correlation between adjacent pixels. This can be useful in a
clinical context. The SSIM~\cite{multiscale_ssim} was designed to
flexible set coefficients for the following three factors: Structure,
Contrast and Intensity. We observed that in many cases, our
qualitative results (e.g., when the standard TV regularization method
outperforms FDK) do not correspond favourably to the default SSIM settings.  We
therefore assigned the following coefficients to the factors
Structure, Contrast, and Intensity respectively: $0.7,0.2,0.1$. Our
results are optimized for structure-focussed SSIM, but it can be
verified that in all cases for the various datasets considered, our
results are favourable with either the default metric, i.e, with
coefficients $1.0,1.0,1.0$ or with our structure-focused metric
wherein we assign a relatively higher weightage to structure
preservation.

%The reason for emphasizing the structure with an
%exponent of 0.7 stems from the optimization process since the
%intensity span (and, in general, the histogram) of reconstructed volumes
%differ across various methods and solvers.

Finally, for a fair comparison in order to not distort metrics,
we report these values in what we believe is a reasonable area of
``new regions''. In particular, these regions of interest (RoI) are
obviously not known in advance, and is thus appropriate for a ``test''.

% \subsection{Tuning of parameters}
\label{sec:tuning_parameters}

Next, we turn to the parameters of the algorithm.  $\lambda_1$,
$\lambda_2$ and $k$ are the three hyper-parameters that need to be
chosen carefully for best results. Since the aim of our experiments is
to demonstrate the benefit of using weighted prior reconstruction, we
proceed to adjust these parameters by (as mentioned earlier) assuming
the ground-truth to be known.

Specifically, $\lambda_1$ was tuned to maximize the SSIM of the
complete reconstructed test volume using the TV-only regularizer.
It's important to note that we retain this value of $\lambda_1$ for
the spatially-varying prior-based reconstruction, i.e., we \emph{do
  not} adjust this value for our spatially-varying method, and,
neither do we know the target ROI where the metric is going to be
finally employed.  With the already chosen optimal $\lambda_1$, we
apply our method for a range of $\lambda_2$ values and select the one
that gives the best SSIM with reference to the ground
truth. %The value of $\lambda_2$ influences the amount of artefacts that can be removed by the use of object-prior at the expense of its dominance in new regions. %This value was found to lie between $(0,3)$ for our datasets.
%In principle, one could have jointly optimized both $\lambda_1$ and
%$\lambda_2$ to get even better results compared to the one we have in
%Sections~\ref{sec:results_with_imaging_model},
%and~\ref{sec:results_without_imaging_model}.  
We note that in practice, however, since ground-truth will never be
available, these parameters must be tuned using only the set of
templates available.  One of the templates can be assumed to be a
pseudo-test, and a grid search can be performed to get the best
possible hyperparameter values. These values can then be used for
reconstructing the `real' test volume.

%in the nvone may select $\lambda_2$ omnisciently only while imaging a
%particular class of object (say `sprouts') for the first time, and
%thereafter retain the same $\lambda_2$ while imaging other objects of
%the same class in future.
